Iterative forecasting and the trap of self-fulfilling prophecies

### 2021-04-02 manuscript/manuscript.Rmd
:pen:

scale_colour_discrete <- function(...) ggthemes::scale_colour_solarized()
scale_fill_discrete <- function(...) ggthemes::scale_fill_solarized()
pal <- ggthemes::solarized_pal()(8)
txtcolor <- "#586e75"
```
```{r, include=FALSE}
rmarkdown::render("appendix.Rmd")
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, dev="cairo_pdf")
```

<!-- I think the introduction could have a clearer storyline and better introduce some of the ideas you bring up later on in the methods/results. A quick outline idea:

  - Paragraph1: Model-based forecasts have become a cornerstone of applied science in disciplines as diverse as atmospheric science [weather?], economics [stock markets?], and ecology [dietz]. Seeking to inform a variety of decisions, near-term forecasting in these diverse fields has  simultaneously been encouraged by policy-makers [CITE?] and enabled by the rapid and recent increase in data availability and computational methods leading to a rapid expansion of thier use (or something...)

   - Paragraph 2: Introduce ecological decision making under uncertainty, rapid global change, etc. (kind of like your current opening bit)

  - Paragraph 3: But do better forecast always lead to better decisions?  Because model-based forecasts frequently play an important role in decision-making,it is commonly assumed [e.g. @Walters1981; @Clark2001; @Dietze2018] that this approach for addressing model uncertainty will also improve decision-making outcomes. 
            - While the literature has largely addressed issues of overfittting that might lead forecasts to misguide decisions, proper scoring methods blah blah [...introduce this concept]. 
            - Beyond overfitted models,... [maybe add something about Value of Information literature here?]

  - Paragraph 4: Your current paragraph on "I illustrate..." (I'd add into that paragraph something about the fact that you explore adaptive management?)

A second idea on framing: this maybe is a to divergent from the main point (or leads you into a post-modernist narrative that you'd prefer to avoid...) but it seems like you could reframe the whole thing as an argument for embracing an inclusive process of resource management that acknowledges pluralism.  
  (1) Policy makers often think "scientists" hold knowledge of "an environmental reality"
  (2) Despite this not being true (scientist disagree on a lot of things), even when "science" points to a more likely reality, that might be off in ways that can fundementally misguide decisions. 
  (3) The problem is deeper than acknowledging a "rashamon set" of models or multiple possible descriptions of of reality. Sometimes what appears closer to reality is actually off in a way that is critical to the decision.
-->

<!-- Open on real-world issues, uncertainty, particularly model uncertainty as key theme.  -->
Global change issues are complex and outcomes are difficult to predict  [@Clark2001]. 
To guide decisions in an uncertainty world, researchers and decision makers 
may consider a range of alternative plausible models to better reflect 
what we do and do not know about the processes involved [@Polasky2011].  Forecasts or
predictions from possible models can indicate what outcomes are most likely to result
under what decisions or actions. This has made model-based forecasts a cornerstone 
for scientifically based decision making.  
By comparing outcomes predicted by a model to future observations, 
a decision maker can not only _plan_ for the uncertainty, but also _learn_ which models are most trustworthy.  The value of iterative learning has long been reflected in the theory of 
adaptive management [@Walters1978] as well as in actual adaptive management practices such as 
Management Strategy Evaluation (MSE) [@Punt2016] used in fisheries, and is a central tenant
of a rapidly growing interest in ecological forecasting [@Dietze2018].
But, do iterative learning approaches always lead to better decisions?

@@

Iterative learning approaches such as adaptive management or iterative forecasting are
particularly compelling because they address a different reason why seemingly-accurate
models can lead to poor outcomes: the problem of overfitting.  When models are estimated
from the data they seek to describe, the model may over-fit the data, making the data
seem even more likely than it would be under the true process [@Burnham1998].
Over-fit models may underestimate uncertainty and make poor predictions about future
outcomes [@Ginzburg2004]. Because any iterative learning compares models to future outcomes,
overfitting those outcomes is impossible.  This concept was rigorously formalized
by @Gneiting2007's proof of "proper" scoring rules. By definition, under a proper 
scoring rule, no probabilistic prediction $Q(x)$ can score better, on
average, than that of the underlying process, $P(x)$.  @Gneiting2007 further shows which
techniques for evaluating forecast predictions do an do not satisfy this condition, i.e. which
cannot be over-fit. Adaptive management is based on equally secure footing because
model predictions are again compared to future outcomes not used to fit the model.
Instead of scoring and selecting among alternative models, adaptive management 
considers probabilities over all models [@Walters1978].  These two approaches are
particularly compelling because they can both reduce uncertainty and avoid over-fitting.
My example is not meant to undercut the importance of these approaches.  Previous
work has long acknowledged the panelope of ways in which iterative learning or other
model-based decision making can go astray due to conflicting incentives,
implementation errors, or lack of resources for monitoring and updating [e.g. @Ludwig1993].
Here, the problem is more fundamental.

<!-- Haven't really queued up the idea that I will present two distinct approaches that both fail.  need to more explicitly introduce and justify the two approaches-->

<!--

A wide range of paradigms are available for approaching the issue of decision-making under uncertainty. These approaches can roughly be divided into two groups: statistical approaches and adaptive management approaches.  The first group, "statistical approaches," seeks to maximize some statistical metric (such as goodness-of-fit or predictive accuracy) in determining which model(s) will drive decisions. In contrast, adaptive management approaches seek to select actions which maximize the decision-maker's expected net utility over

In the first group, I focus on evaluation using "proper" scoring rules as defined by @Gneiting2007, rather than potentially more familiar model comparisons such as $r^2$, likelihood, or information criteria [@Burnham1998] because proper scoring rules are more robust  (see @Gneiting2007 for comparison and how the approaches relate under appropriate assumptions). @Gneiting2007 provides a rigorous proof of scoring rules that have the desirable property of being "proper", that is, rules for which no model predicting the distribution of future outcomes, $Q(x)$ can achieve a better average score than the true model $P(x)$. Unlike likelihood or other goodness-of-fit scores alone, it is impossible (in expectation) to overfit the proper score -- no model model can out-perform the true model. Note that strictly proper scoring rules score _probabilistic forecasts_ and not just point predictions, favoring models which accurately reflect the uncertainty over those which under-estimate it.  These features have made proper scoring rules for probabilistic forecasts a successful and popular approach for addressing model uncertainty in many other areas [@Gneiting2014; @Raftery2016] and a promising tool for evaluation of ecological forecasts [@Dietze2018].

For the second group, decision-theoretic approaches, I focus on the example of adaptive management
Decision-theoretic approaches include scenario analysis, resilience thinking, optimal control and related methods [@Polasky2011], which have a long history in ecology and particularly in fisheries management. One of the most influential of these is _adaptive management_ [sensu @Walters1978], in which a manager seeks to both reduce uncertainty over time while also achieving the best outcomes given current knowledge.  While the term today is frequently used in a looser sense, adaptive management as originally developed can be considered an example of optimal control under model uncertainty [@Walters1981; @Smith1981].  In this approach, a manager assigns probabilities to each of the possible models under consideration, i.e. models 1 & 2.  The expected utility of any action reflects both the intrinsic uncertainty over future states under either model (process uncertainty) and the manager's uncertainty over the choice of models (or parameter values). Unlike the forecast comparison, an adaptive management approach explicitly considers the utility function, Eqn \eqref{utility}, which it seeks to maximize by integrating over model uncertainty. After observing the consequences of the action, the manager updates the posterior probabilities that each model is correct, typically by Bayes rule [e.g. @Walters1981; @Smith1981; @Ludwig1982; @Punt2016]. The decision strategy is then re-evaluated in light of this revised uncertainty.  Adaptive management may be either passive or active. Under passive adaptive management, the decision-maker chooses the action which maximizes that expected future utility.  Under active adaptive management, the decision-maker may chose 'exploratory' actions which are not optimal under the current uncertainty but may lead to more rapidly decreasing the uncertainty in the future [@Walters1978]. In practice, many managers are reluctant to employ exploratory strategies, so passive adaptive management approaches such as as Management Strategy Evaluation (MSE) are more common [@Punt2016].

-->

@@

```{r figure1, fig.width=7, fig.height=5, fig.cap = "Forecast performance of each model.  Panels A, B: Step ahead predictions of stock size under unfished (A) and fished (B) scenarios. Error bars indicating the 95% confidence intervals around each prediction, while stars denote the observed value in that year.  Because the models make different decisions each year in the fished scenario, the observed stock size in year 2, 3, etc under the management of model 1 (blue stars) is different from that under model 2 (red stars).  Panels C, D: corresponding distribution of proper scores across all predictions (100 replicates of 100 timesteps). Higher scores are better, confirming that model 2 makes the better forecasts."}
predictions <- read_csv("../data/predictions.csv") %>% mutate(model = as.character(model))

@@

<!-- replacing step-ahead with n-step ahead would not matter-->

@@

<!--
Any of these adaptive management approaches proves to be maladaptive under the simple example of model uncertainty considered here.  That is, the manager derives lower utility (here, economic yield), and the fish stock is also surpressed to a lower biomass than would be achieved if an identical management approach without any adaptive updating to model uncertainty were employed.  Put another way, the "value of information" gained from future observations of stock in response to any management action is actually negative.

Owing to the greater complexity involved in many fisheries models, a typical MSE would evaluate a fixed set of possible strategies rather than solve a sequential decision problem [@Marescot2013] for the optimal sequence of actions, but the central premise of iteratively updating model posterior probabilities remains the same.  By limiting ourselves to the simpler models considered here, we are able to perform a passive adaptive management analysis of the full sequential decision problem, analgous to earlier examples [@Walters1981; @Smith1981; @Ludwig1982], which ensures the result is not an artifact of considering too narrow a set of possible policies (e.g. only constant-mortality policies).

-->

@@

```{r figure3, fig.height=5, fig.width=8, fig.cap="Adaptive management under model uncertainty.  Solid lines trace the trajectories of the state (fish stock, circles) and action (harvest quota, triangles), under adaptive management (learning).  Dotted lines trace the corresponding trajectories if iterative learning is omitted, leaving the prior belief fixed throughout the simulation (planning).   Color indicates the belief that model 1 is correct (blue), with an intial prior belief of 99%.  Panel A: Management over the two candidate models, Model 1 and Model 2. Within a single iteration of adaptive management, the belief over models switches from a prior belief that heavily favored model 1 to a posterior that favors model 2 with near certainty.  Future iterations reinfornce the belief in model 2, resulting in both depressed harvests and low stock sizes (solid lines).  If no iterative learning updates are performed, stock sizes and realized harvests (and thus economic profit) are both higher. Panel B: given 42 candidate models over a broad range of parameter values, adaptive management quickly reduces the probability on model 1, and substantially underperforms management without learning (dotted lines). While outcomes improve marginally relative to the two-model case (figure A) they remain significantly worse than had no iterative learning been included."}
am <- read_csv("../data/am.csv")
fig3a <- am %>%  filter(time <=20) %>% 
  pivot_longer(c(stock, quota), values_to="stock", names_to="key") %>%
  mutate(key = factor(key, levels = c("stock", "quota"))) %>%
  ggplot(aes(time, stock, shape = key, group = interaction(method,key))) + 
  geom_line(aes(lty=method), col = "gray40", show.legend = FALSE) + 
  geom_point(aes(col = belief), size=2, show.legend = FALSE) +
  scale_colour_gradient(limits = c(0,1), low = pal[4], high = pal[1]) +
  ylab("fish stock") + labs(subtitle="A.")

@@

<!-- 
First: Intuition for the result.
  - See that model 1 captures the key feature, while model 2 is just 'closer to the curve'
  - See that this is a generic truth about decision-making: there's always a Model 1
  - This is not about over-fitting.
-->

<!-- quick summary of what was demonstrated -->
Given this simple decision problem in which one of the two models leads to effectively optimal ecological and economic outcomes, current approaches invariably choose the other.
Moreover, a decision maker employing an adaptive management or iterative forecasting assessment such as those considered here would have no way of realizing that the outcomes they experienced were in fact sub-optimal.
In both approaches, the manager quickly concludes that model 1 is entirely implausible, while finding that model 2 is remarkably accurate at predicting future values.
This problem is not addressed by re-estimating parameters (equivalently, considering a larger suite of models spanning a wide range of possible $K$ and $r$ values): which improves only marginally over the outcome of considering only two models [Fig 3B].
Both iterative forecast evaluation and the adaptive management approaches to reducing model uncertainty lead to management becoming trapped in a self-fulfilling prophecy:
holding the fish population at an unproductively low biomass suggested by model 2 while becoming ever more convinced that model is suitable. 
Without access to the true model, none of our methods for model choice or reducing model uncertainty can break this trap.

@@

```{r figure4,  fig.cap="Panel A: Population growth curves of each model. The positive equilibrium of each model occurs where the curve crosses the horizontal axis. Note that while Model 2 is a better approximation to the truth (Model 3), Model 1 better approximates the stock size which leads to maximum growth.  Panel B: The optimal control policy under Model 1 is nearly identical to that under the true Model 3, while the optimal policy under Model 2 supresses stock to a much lower escapement level.", fig.width=8}
# Fig 4
model_curves <- read_csv("../data/model_curves.csv") %>% mutate(model = as.character(model))
policies <- read_csv("../data/policies.csv") %>% mutate(model = as.character(model))

@@

<!--
So what?
- This is different than previous work: e.g. VOI is not zero, it's negative here.
- Model 1 is not a unicorn: we cannot rule out these situations in real world (particularly ecology where we don't actually do much iterative updating in practice)
- 
-->

@@

<!-- Model free management: what would it look like? -->
<!-- For example, a simple approach could gradually increase harvest from 0 as long as the observed recruitment increases relative to previous values.  This corresponds to a local search for the peak growth-rate from above. This strategy is optimal for the model considered here, at least under small noise, but is not robust to growth rates with local optima, nor is it optimal during a possibly-very-long transient period of the search.   -->

<!-- Correlary: Neither accurate forecasting nor effective outcomes are sufficient grounds to assert model validity. (meh, that's just 'all models are wrong, some are useful' for certain things)   -->

@@

<!--
Is this result merely an artifact of differing objectives?  @Gneiting2007's proper scoring rules are designed to select models which make the best forecast, and Model 2 really is the best choice for that task.  However, the adaptive management approach explicitly seeks to maximize expected utility, integrating over the uncertainty in the model, and yet it evolves away from Model 1 which would achieve that goal and settles on Model 2.  Note that this issue is not resolved by updating the learning step to reflect only the immediate reward -- it is in fact easy to see that so-called greedy algorithms would take the largest harvest possible and never reach the sustainable yield achieved by lower harvest rates of Model 1. To select Model 1 over alternatives like Model 2 which make better predictions but lead to worse outcomes requires a more long-term approach that forgoes iterative updating of probabilities as new data becomes available.  Note that this is the opposite recommendation of _adaptive_ management [@Walters1978] or _iterative_ forecasting [@Dietze2018].
-->

<!--

The open problem is simply to propose an approach to model uncertainty which would select model 1
over model 2 (i.e. choosing among the suite of available models, the one that gives the better 
decisions.)

-->

>>>>

scale_colour_discrete <- function(...) ggthemes::scale_colour_solarized()
scale_fill_discrete <- function(...) ggthemes::scale_fill_solarized()
pal <- ggthemes::solarized_pal()(8)
txtcolor <- "#586e75"
```

```{r, include=FALSE}
rmarkdown::render("appendix.Rmd")
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, dev="cairo_pdf", fig.height=5, fig.width=7.5)
```

Global change issues are complex and outcomes are difficult to predict  [@Clark2001].
To guide decisions in an uncertainty world, researchers and decision makers may consider a range of alternative plausible models to better reflect what we do and do not know about the processes involved [@Polasky2011].
Forecasts or predictions from possible models can indicate what outcomes are most likely to result under what decisions or actions.
This has made model-based forecasts a cornerstone for scientifically based decision making.
By comparing outcomes predicted by a model to future observations, a decision maker can not only _plan_ for the uncertainty, but also _learn_ which models are most trustworthy. 
The value of iterative learning has long been reflected in the theory of adaptive management [@Walters1978] as well as in actual adaptive management practices such as Management Strategy Evaluation (MSE) [@Punt2016] used in fisheries, and is a central tenant of a rapidly growing interest in ecological forecasting [@Dietze2018].
But, do iterative learning approaches always lead to better decisions?

@@

Iterative learning approaches such as adaptive management or iterative forecasting [@Dietze2018] are particularly compelling because they address a different reason why seemingly-accurate models can lead to poor outcomes: the problem of over-fitting.
When models are estimated from the data they seek to describe, the model may over-fit the data, making the data seem even more likely than it would be under the true process [@Burnham1998].
Over-fit models may underestimate uncertainty and make poor predictions about future outcomes [@Ginzburg2004].
Because any iterative learning compares models to future outcomes, overfitting those outcomes is impossible.
This concept was rigorously formalized by @Gneiting2007's proof of "proper" scoring rules.
By definition, under a proper scoring rule, no probabilistic prediction $Q(x)$ can score better, on average, than that of the underlying process, $P(x)$.
@Gneiting2007 further shows which techniques for evaluating forecast predictions do an do not satisfy this condition, i.e. which cannot be over-fit.
Adaptive management is based on equally secure footing because model predictions are again compared to future outcomes not used to fit the model.
Instead of scoring and selecting among alternative models, adaptive management considers probabilities over all models [@Walters1978].
These two approaches are particularly compelling because they can both reduce uncertainty and avoid over-fitting.
My example is not meant to undercut the importance of these approaches.
Previous work has long acknowledged the panelope of ways in which iterative learning or other model-based decision making can go astray due to conflicting incentives implementation errors, or lack of resources for monitoring and updating [e.g. @Ludwig1993].
Here, the problem is more fundamental.

@@

```{r figure1, fig.cap = "Forecast performance of each model.  Panels A, B: Step ahead predictions of stock size under unfished (A) and fished (B) scenarios. Error bars indicating the 95% confidence intervals around each prediction, while stars denote the observed value in that year.  Because the models make different decisions each year in the fished scenario, the observed stock size in year 2, 3, etc under the management of model 1 (blue stars) is different from that under model 2 (red stars).  Panels C, D: corresponding distribution of proper scores across all predictions (100 replicates of 100 timesteps). Higher scores are better, confirming that model 2 makes the better forecasts."}
predictions <- read_csv("../data/predictions.csv") %>% mutate(model = as.character(model))

@@

@@

@@

```{r figure3, fig.cap="Adaptive management under model uncertainty.  Solid lines trace the trajectories of the state (fish stock, circles) and action (harvest quota, triangles), under adaptive management (learning).  Dotted lines trace the corresponding trajectories if iterative learning is omitted, leaving the prior belief fixed throughout the simulation (planning).   Color indicates the belief that model 1 is correct (blue), with an intial prior belief of 99%.  Panel A: Management over the two candidate models, Model 1 and Model 2. Within a single iteration of adaptive management, the belief over models switches from a prior belief that heavily favored model 1 to a posterior that favors model 2 with near certainty.  Future iterations reinfornce the belief in model 2, resulting in both depressed harvests and low stock sizes (solid lines).  If no iterative learning updates are performed, stock sizes and realized harvests (and thus economic profit) are both higher. Panel B: given 42 candidate models over a broad range of parameter values, adaptive management quickly reduces the probability on model 1, and substantially underperforms management without learning (dotted lines). While outcomes improve marginally relative to the two-model case (figure A) they remain significantly worse than had no iterative learning been included."}
am <- read_csv("../data/am.csv")
fig3a <- am %>%  filter(time <=20) %>% 
  pivot_longer(c(stock, quota), values_to="stock", names_to="key") %>%
  mutate(key = factor(key, levels = c("stock", "quota"))) %>%
  ggplot(aes(time, stock, shape = key, group = interaction(method,key))) + 
  geom_line(aes(lty=method), col = "gray40", show.legend = FALSE) + 
  geom_point(aes(col = belief), size=2, show.legend = FALSE) +
  scale_colour_gradient(limits = c(0,1), low = pal[4], high = pal[1]) +
  ylab("fish stock") + labs(subtitle="A.")

@@

<!-- quick summary of what was demonstrated -->
Given this simple decision problem in which one of the two models leads to effectively optimal ecological and economic outcomes, current approaches invariably choose the other.
Moreover, a decision maker employing an adaptive management or iterative forecasting assessment such as those considered here would have no way of realizing that the outcomes they experienced were in fact sub-optimal.
In both approaches, the manager quickly concludes that model 1 is entirely implausible, while finding that model 2 is remarkably accurate at predicting future values.
This problem is not addressed by re-estimating parameters (equivalently, considering a larger suite of models spanning a wide range of possible $K$ and $r$ values): which improves only marginally over the outcome of considering only two models [Fig 3B].
Both iterative forecast evaluation and the adaptive management approaches to reducing model uncertainty lead to management becoming trapped in a self-fulfilling prophecy:
holding the fish population at an unproductively low biomass suggested by model 2 while becoming ever more convinced that model is suitable. 
Without access to the true model, none of our methods for model choice or reducing model uncertainty can break this trap.
This should not be mistaken as a critique of adaptive management or iterative forecasting specifically -- other model choice approaches such as goodness-of-fit, information criteria or cross-validation would all prefer model 2 as well.

@@

```{r figure4,  fig.cap="Panel A: Population growth curves of each model. The positive equilibrium of each model occurs where the curve crosses the horizontal axis. Note that while Model 2 is a better approximation to the truth (Model 3), Model 1 better approximates the stock size which leads to maximum growth.  Panel B: The optimal control policy under Model 1 is nearly identical to that under the true Model 3, while the optimal policy under Model 2 supresses stock to a much lower escapement level."}
# Fig 4
model_curves <- read_csv("../data/model_curves.csv") %>% mutate(model = as.character(model))
policies <- read_csv("../data/policies.csv") %>% mutate(model = as.character(model))

@@

@@

@@

### 2021-04-02 manuscript/scratch.Rmd
:pen:

@@

>>>>

<!--

A wide range of paradigms are available for approaching the issue of decision-making under uncertainty. These approaches can roughly be divided into two groups: statistical approaches and adaptive management approaches.  The first group, "statistical approaches," seeks to maximize some statistical metric (such as goodness-of-fit or predictive accuracy) in determining which model(s) will drive decisions. In contrast, adaptive management approaches seek to select actions which maximize the decision-maker's expected net utility over

In the first group, I focus on evaluation using "proper" scoring rules as defined by @Gneiting2007, rather than potentially more familiar model comparisons such as $r^2$, likelihood, or information criteria [@Burnham1998] because proper scoring rules are more robust  (see @Gneiting2007 for comparison and how the approaches relate under appropriate assumptions). @Gneiting2007 provides a rigorous proof of scoring rules that have the desirable property of being "proper", that is, rules for which no model predicting the distribution of future outcomes, $Q(x)$ can achieve a better average score than the true model $P(x)$. Unlike likelihood or other goodness-of-fit scores alone, it is impossible (in expectation) to overfit the proper score -- no model model can out-perform the true model. Note that strictly proper scoring rules score _probabilistic forecasts_ and not just point predictions, favoring models which accurately reflect the uncertainty over those which under-estimate it.  These features have made proper scoring rules for probabilistic forecasts a successful and popular approach for addressing model uncertainty in many other areas [@Gneiting2014; @Raftery2016] and a promising tool for evaluation of ecological forecasts [@Dietze2018].

For the second group, decision-theoretic approaches, I focus on the example of adaptive management
Decision-theoretic approaches include scenario analysis, resilience thinking, optimal control and related methods [@Polasky2011], which have a long history in ecology and particularly in fisheries management. One of the most influential of these is _adaptive management_ [sensu @Walters1978], in which a manager seeks to both reduce uncertainty over time while also achieving the best outcomes given current knowledge.  While the term today is frequently used in a looser sense, adaptive management as originally developed can be considered an example of optimal control under model uncertainty [@Walters1981; @Smith1981].  In this approach, a manager assigns probabilities to each of the possible models under consideration, i.e. models 1 & 2.  The expected utility of any action reflects both the intrinsic uncertainty over future states under either model (process uncertainty) and the manager's uncertainty over the choice of models (or parameter values). Unlike the forecast comparison, an adaptive management approach explicitly considers the utility function, Eqn \eqref{utility}, which it seeks to maximize by integrating over model uncertainty. After observing the consequences of the action, the manager updates the posterior probabilities that each model is correct, typically by Bayes rule [e.g. @Walters1981; @Smith1981; @Ludwig1982; @Punt2016]. The decision strategy is then re-evaluated in light of this revised uncertainty.  Adaptive management may be either passive or active. Under passive adaptive management, the decision-maker chooses the action which maximizes that expected future utility.  Under active adaptive management, the decision-maker may chose 'exploratory' actions which are not optimal under the current uncertainty but may lead to more rapidly decreasing the uncertainty in the future [@Walters1978]. In practice, many managers are reluctant to employ exploratory strategies, so passive adaptive management approaches such as as Management Strategy Evaluation (MSE) are more common [@Punt2016].

-->

<!--
Any of these adaptive management approaches proves to be maladaptive under the simple example of model uncertainty considered here.  That is, the manager derives lower utility (here, economic yield), and the fish stock is also surpressed to a lower biomass than would be achieved if an identical management approach without any adaptive updating to model uncertainty were employed.  Put another way, the "value of information" gained from future observations of stock in response to any management action is actually negative.

Owing to the greater complexity involved in many fisheries models, a typical MSE would evaluate a fixed set of possible strategies rather than solve a sequential decision problem [@Marescot2013] for the optimal sequence of actions, but the central premise of iteratively updating model posterior probabilities remains the same.  By limiting ourselves to the simpler models considered here, we are able to perform a passive adaptive management analysis of the full sequential decision problem, analgous to earlier examples [@Walters1981; @Smith1981; @Ludwig1982], which ensures the result is not an artifact of considering too narrow a set of possible policies (e.g. only constant-mortality policies).

-->

@@

<!--
Is this result merely an artifact of differing objectives?  @Gneiting2007's proper scoring rules are designed to select models which make the best forecast, and Model 2 really is the best choice for that task.  However, the adaptive management approach explicitly seeks to maximize expected utility, integrating over the uncertainty in the model, and yet it evolves away from Model 1 which would achieve that goal and settles on Model 2.  Note that this issue is not resolved by updating the learning step to reflect only the immediate reward -- it is in fact easy to see that so-called greedy algorithms would take the largest harvest possible and never reach the sustainable yield achieved by lower harvest rates of Model 1. To select Model 1 over alternatives like Model 2 which make better predictions but lead to worse outcomes requires a more long-term approach that forgoes iterative updating of probabilities as new data becomes available.  Note that this is the opposite recommendation of _adaptive_ management [@Walters1978] or _iterative_ forecasting [@Dietze2018].
-->

<!--

The open problem is simply to propose an approach to model uncertainty which would select model 1
over model 2 (i.e. choosing among the suite of available models, the one that gives the better 
decisions.)

-->
